A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
association rules slide

\documentclass[xcolor=dvipsnames,professionalfonts,smaller,presentation]{beamer} 
\usecolortheme[named=Brown]{structure} 
\useoutertheme{miniframes}
\usetheme{Malmoe}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[portuguese]{babel}
\usepackage[latin1]{inputenc}
\usepackage{alltt}
\usepackage{moreverb}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{lastpage}
\usepackage{url}
\usepackage{float}
\usepackage{subfigure}

@@

\frame
{
    \frametitle{Association Rules}
}

>>>>

\documentclass[xcolor=dvipsnames,professionalfonts,smaller,presentation]{beamer} 
\usecolortheme[named=Brown]{structure} 
\useoutertheme{miniframes}
\usetheme{Malmoe}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[portuguese]{babel}
\usepackage[latin1]{inputenc}
\usepackage{alltt}
\usepackage{moreverb}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{lastpage}
\usepackage{array}
\usepackage{url}
\usepackage{float}
\usepackage{subfigure}

@@

\frame
{
    \frametitle{Association Rules}

    \begin{itemize}
      \item <1-> Association rules can be used to discover interesting relations and patterns between attributes.

    \end{itemize}

    \begin{table}[ht]
        \begin{center}
        \scalebox{1.0}{

        \begin{tabular}{ | m{5cm} | c | c | c | }
        \hline
        \textbf{Rule / LHS} & \textbf{RHS} & \textbf{Support} & \textbf{Confidence} \\ \hline
        \footnotesize{age=young, hours\_per\_week=part\_time} & $<$50K & 0.05730782 & 1 \\ \hline
        \footnotesize{marital\_status=never\_married, relationship=own\_child, hours\_per\_week=part\_time} & $<$50K & 0.04689659 & 1 \\ \hline
        \footnotesize{age=young, relationship=own\_child, hours\_per\_week=part\_time} & $<$50K & 0.04404042 & 1 \\ \hline
        \footnotesize{relationship=husband, capital\_gain=high} & $>$50K & 0.02251159 & 0.9918809 \\ \hline
        \footnotesize{relationship=husband, race=white, sex=male, capital\_gain=high} & $>$50K & 0.02063819 & 0.9926145 \\ \hline
        \end{tabular}}
        \label{tbl:arules_income}
        \end{center}
    \end{table}
}
